decompr: GVC decomposition in R

### 2015-03-11 draft.Rnw
break line 668 to clarify possible errors with \LuaTeX command. recompile after adding pandoc to colophon

\section*{Colophon}
This paper was written in a combination of R \parencite{core2014r} and \LaTeX ~\parencite{lamport1986document}, specifically \LuaTeX ~\parencite{hagen2005luatex} with biblatex and biber \parencite{lehman2006biblatex} for citations, using Sweave syntax \parencite{leisch2003sweave} and compiled using knitr \parencite{yihui2013knitr}.

>>>>

\section*{Colophon}
This paper was written in a combination of R \parencite{core2014r} and \LaTeX ~\parencite{lamport1986document},
specifically \LuaTeX ~\parencite{hagen2005luatex}, with biblatex and biber \parencite{lehman2006biblatex} for citations,
using Sweave syntax \parencite{leisch2003sweave} and compiled using knitr \parencite{yihui2013knitr} and Pandoc \parencite{macfarlane2012pandoc}.
